A Documentary History of \\ the Nock Combinator Calculus

### 2025-07-06 mss.tex
PosT

%%MANUSCRIPT
\title{Hot Nock:  A History of the Nock Combinator Calculus}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

@@

\begin{itemize}
  \item  Turing-complete.  Put formally, Turing completeness (and thus the ability to evaluate anything we would call a computation) is exemplified by the $μ$-recursive functions \citep{WikipediaMuRecursive}.  In practice, these amount to operations for constant, increment, variable access, program concatenation, and looping \citep{Raphael2012}.  Nock supports these directly through its primitive opcodes.
  % WikipediaMuRecursive https://en.wikipedia.org/wiki/General_recursive_function
  % Raphael2012 https://cs.stackexchange.com/questions/991/are-there-minimum-criteria-for-a-programming-language-being-turing-complete

>>>>

%%MANUSCRIPT
\title{A Documentary History of \\ the Nock Combinator Calculus}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

@@

\begin{itemize}
  \item  \sloppy Turing-complete.  Put formally, Turing completeness (and thus the ability to evaluate anything we would call a computation) is exemplified by the $\mu$-recursive functions.  In practice, these amount to operations for constant, \mbox{increment}, variable access, program concatenation, and looping \citep{Raphael2012}.  Nock supports these directly through its primitive opcodes.
  % WikipediaMuRecursive https://en.wikipedia.org/wiki/General_recursive_function
  % Raphael2012 https://cs.stackexchange.com/questions/991/are-there-minimum-criteria-for-a-programming-language-being-turing-complete
